---
title: "p8105_hw5_jf3355"
author: "Jiahao Fan"
date: "11/19/2021"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

##Problem 1
```{r}
homicide_df = 
  read.csv("homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```
## This dataset has 14 columns and 52178 rows. All variables represent the information about victim.

#Focus on city Baltimore, MD
```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
    )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```

##All cities
```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
  city_df %>%
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved),
              n = city_summary %>% pull(n))
  return(city_test)
  
}
homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

```{r}
results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
results_df
```

#create a plot showing estimates and confidence intervals
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```
##Problem2
#Create a tidy dataframe containing data from all participants,including the subject ID, arm, and observations over time:
```{r}
file_df = 
  tibble(path = list.files("data")) %>% 
  mutate(data = 
           map(path, ~read.csv(str_c("data/", .x)))) %>% 
  unnest(data)

study_df =
  file_df %>% 
  separate(path, into = c('arm', 'id'), sep = "_") %>%
  mutate(id = str_replace(id,".csv","")) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% 
  mutate(
    week = as.integer(week),
    arm = recode(arm, "con"= "Control", "exp" = "Experiment"),
    arm = factor(arm),
    id = factor(id)
  )
study_df
```
#Make a spaghetti plot showing observations on each subject over time
```{r}
study_df %>%
  ggplot(aes(x = week, y = observation, color = id, linetype = arm)) +
  geom_line() + 
  labs(
    title = "Observation of Control and Experimental Groups Over 8 Weeks",
    x = "Week",
    y = "Observation")
```
#Comment: From the plot, we see that there is no significant linear relationship between them, and after week 7, there is a separation between them.
##Problem 3
